Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-06-16 ms.tex
Update on Overleaf.

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_epic_cost_analysis_SKA1-low.pdf}
{figures/1D_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the EPIC architecture at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I} station (cyan lines). The spatial FFT cost in Equation~(\ref{eqn:intra-station-pol-hol-img-epic-LA}) denoted by black dashed lines dominates the squaring (pink dot-dashes) and temporal averaging (blue dot-dashes) costs in Equation~(\ref{eqn:intra-station-opt-polarimetric-direct-img-LA}). The gridding operation (black dotted lines) in Equation~(\ref{eqn:intra-station-pol-hol-img-epic-LA}) contributes even lesser to the cost budget. 
\label{fig:1D-incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure}

@@

Figure~\ref{fig:multidim-incoherent-compcost-XFFT-LAMBDA-I} shows the covariant view of the total computational cost density per station per voxel for the correlator FFT architecture taken two station parameters at a time while keeping the rest fixed at the nominal values of a \texttt{LAMBDA-I} station denoted by grey dashed lines. The variation in the cost per voxel for $t_\textrm{acc}=1$~ms is dominated by the gridding cost, displaying the same trends observed in Figure~\ref{fig:1D-incoherent-compcost-XFFT-LAMBDA-I}. Figure~\ref{fig:multidim-incoherent-relative-compcost-XFFT-LAMBDA-I} shows the ratio of the computational cost of the XFFT architecture relative to the voltage beamforming architecture in Figure~\ref{fig:multidim-incoherent-compcost-BF-LAMBDA-I}. It is clearly noted that the cost of the XFFT architecture is less expensive than the VBF in most of the parameter space, particularly for larger $D_\textrm{s}/D_\textrm{a}$. For the chosen \texttt{LAMBDA-I} parameters (gray dashed lines), the XFFT cost is roughly equal to that of voltage beamforming.

@@

>>>>

\begin{figure}
\includegraphics[width=0.99\linewidth]
% {figures/1D_epic_cost_analysis_SKA1-low.pdf}
{figures/1D_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the EPIC architecture at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I} station (cyan lines). The spatial FFT cost in Equation~(\ref{eqn:intra-station-pol-hol-img-epic-LA}) denoted by black dashed lines dominates the squaring (pink dot-dashes) and temporal averaging (blue dot-dashes) costs in Equation~(\ref{eqn:intra-station-opt-polarimetric-direct-img-LA}). The gridding operation (black dotted lines) in Equation~(\ref{eqn:intra-station-pol-hol-img-epic-LA}) contributes even lesser to the cost budget. 
\label{fig:1D-incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure}

@@

@@

Figure~\ref{fig:multidim-incoherent-compcost-XFFT-LAMBDA-I} shows a covariant view of the total computational cost density per station per voxel for the correlator FFT architecture taken two station parameters at a time while keeping the rest fixed at the nominal values of a \texttt{LAMBDA-I} station denoted by grey dashed lines.

The variation in the cost per voxel for $t_\textrm{acc}=1$~ms is dominated by the gridding cost, displaying the same trends observed in Figure~\ref{fig:1D-incoherent-compcost-XFFT-LAMBDA-I}. Figure~\ref{fig:multidim-incoherent-relative-compcost-XFFT-LAMBDA-I} shows the ratio of the computational cost of the XFFT architecture relative to the voltage beamforming architecture in Figure~\ref{fig:multidim-incoherent-compcost-BF-LAMBDA-I}. It is clearly noted that the cost of the XFFT architecture is less expensive than the VBF in most of the parameter space, particularly for larger $D_\textrm{s}/D_\textrm{a}$. For the chosen \texttt{LAMBDA-I} parameters (gray dashed lines), the XFFT cost is roughly equal to that of voltage beamforming.
